Eliminating prior-bias from sparse-projection tomographic reconstructions

### 2020-07-18 paper/tci.tex
Rearranged dataset figures

\textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
consisted of real circular cone-beam projections from 450 views, each of size
336$\times$156. The corresponding size of the reconstructed volume is
338$\times$338$\times$123. Prior to the first scan, two holes were
drilled on the surface of the specimen. This was followed by four
scans, each after introducing one new cut. The specimen was kept in
the same position throughout the acquisitions. In cases where such an
alignment is not present, all the template volumes must be pre-aligned
before computing the eigenspace. The test must be registered to the
object-prior after its preliminary pilot reconstruction. The ground
truth consists of volumes reconstructed using the Feldkamp-Davis-Kress
(FDK) algorithm~\cite{FDK} from the full set of 450 view
projections. The test volume was reconstructed from a partial set of
45 projections, i.e., $10\%$ of the projection views from which ground
truth was reconstructed.\\

\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}). Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150. The corresponding size of the reconstructed volume is 150$\times$150$\times$100. While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.  Projections were obtained using circular cone beam geometry.  %Further, this alignment can be refined following every update of the reconstructed test volume.
The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views. The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed.
\subsection{Simulated measurements from real-life reconstructed volumes}
\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU, consists of six reconstructed
volumes corresponding to six scans of an in-vivo sprout specimen
imaged at its various stages of growth
(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated
from the given volume of size 130$\times$130$\times$130. The ground
truth consists of FDK reconstructed volumes from a set of 1800 view
projections. The test volume was reconstructed from partial set of 45
projections, i.e., $2.5\%$ of the projection views from which ground
truth was reconstructed.\\

\textbf{Radio-frequency ablation:} We have used this dataset to
illustrate an application where \textit{both} uniform and spatially-varying priors are
useful. The data~\footnote{Source: Tata Memorial
  Centre~\cite{tmh}, Parel, Mumbai.  This is the national
  comprehensive centre for the prevention, treatment, education and
  research in cancer, and is recognized as one of the leading cancer
  centres in India.} consists of simulated parallel beam measurements of 2D slices
of the organ (liver) at different stages of the scan. The details of this study are presented in the next section.

@@

%--------------------------Results on TMH data--------------------------
%------------------RFA 2 data
\begin{figure}[h!]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 2}
    \end{subfigure}
     \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 3}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 4}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 5}
    \end{subfigure}
              \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 6}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 7}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 8}
    \end{subfigure}     
     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver. Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor. (h) the organ after the ablation: this slice is displayed on a separate intensity scale to enable proper viewing of the region marked in green that shows the after-effects of ablating the tumor.} 
\label{fig:RFA2_test_object-prior}
\end{figure}

@@

 %--------------------------------okra data-------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.176\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/test.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:object-prior_test_okra}
\end{figure}
%----------------------------------------------------

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM of the full reconstructed okra volume by various methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline
                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
\textbf{full Volume} & 1 (ideal)                     & 0.83        &  0.87       & \textcolor{red}{0.89}                                                                                   \\ \hline
\end{tabular}
\label{table:okra_ssim_full_volume}
\end{table}
%----------------------------------------------------
\subsubsection{\textbf{Sprouts dataset}}
\label{Sec:sprouts}
 In contrast to the scientific experiment performed for the case of
 the okra where we introduced man-made defects, the changes here are
 purely the work of nature. One of the slices of the reconstructed
 volumes is shown in
 Fig.~\ref{fig:sprouts_3D_results_uniform}. Table~\ref{table:sprouts_ssim_full_volume}
 shows the SSIM of the full reconstructed volumes.  Here again, the
 presence of a unifrom object prior significantly improves the overall
 reconstruction in comparison with the usage of sparsity prior alone.
 The selected 3D ground truth of template volumes, the test volume as
 well as the 3D reconstructions can be seen in the supplementary
 material~\cite{supp_paper}.
%-------------------------sprouts data

\begin{figure}[!h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
\captionsetup{labelformat=empty}
        \caption{}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}\\
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
        right).}
\label{fig:object-prior_test_sprouts}
\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
 %-----------------------------sprouts 3D results
\begin{figure}[!h]
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
%\captionsetup{labelformat=empty}
        \caption{l1-ls}
     \end{subfigure}\\
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Uniform Prior}
     \end{subfigure}
     \caption{3D reconstruction of sprouts from $2.5\%$ projection
       views (b, c) have poor details (d) no new information detected
       (the prior dominates as can be seen in the blue and red
       regions) and (e) new information detected in the regions of
       interest. The reconstructed volumes can be viewed in the supplementary material
       ~\cite{supp_paper}.} 
\label{fig:sprouts_3D_results_uniform}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

@@

\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights:}
%-----------------------------potato data
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
\captionsetup{labelformat=empty}
        \caption{}
\label{fig:potato_test}
     \end{subfigure}
      \caption{Potato dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A1}
\end{figure}

%-----------------------------potato 2D weights
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_fbp30.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_dct30.png}
        \caption{(l1-ls)-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_wavelet30.png}
        \caption{(l1-ls)-Haar}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_art30.png}
        \caption{ART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sart30.png}
        \caption{SART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sirt30.png}
        \caption{SIRT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_all_methods30.png}
        \caption{combined}
     \end{subfigure}
      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $\boldsymbol{V_\text{low}}$) constructed using different reconstruction methods individually (a-f) and collectively (g) by fusing information from all reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}. The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}. }
\label{fig:weights_map_2Dpotato}
\end{figure}
%-----------------------------potato 2D weights
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/cs_dct.png}
        \caption{(l1-ls)-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/cs_wavelet.png}
        \caption{(l1-ls)-Haar}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/art.png}
        \caption{ART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/sart.png}
        \caption{SART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/sirt.png}
        \caption{SIRT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weighted_pca_all_methods30.png}
        \caption{combined}
     \end{subfigure}
      \caption{(a)-(f):Different reconstructions of~\ref{fig:object-prior_test_potato_A1}(d). The magnitude and sharpness of the artefacts is different for each method. (g) Spatially-Varying-prior method that combines weights-map information from all other methods. The SSIM of these reconstructions is shown in Table.~\ref{table:potato_2D_ssim}.} 
\label{fig:reconstructions_diff_methods}
\end{figure}

>>>>

 \textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
consisted of real circular cone-beam projections from 450 views, each of size
336$\times$156. The corresponding size of the reconstructed volume is
338$\times$338$\times$123. Prior to the first scan, two holes were
drilled on the surface of the specimen. This was followed by four
scans, each after introducing one new cut. The specimen was kept in
the same position throughout the acquisitions. In cases where such an
alignment is not present, all the template volumes must be pre-aligned
before computing the eigenspace. The test must be registered to the
object-prior after its preliminary pilot reconstruction. The ground
truth consists of volumes reconstructed using the Feldkamp-Davis-Kress
(FDK) algorithm~\cite{FDK} from the full set of 450 view
projections. The test volume was reconstructed from a partial set of
45 projections, i.e., $10\%$ of the projection views from which ground
truth was reconstructed.\\
 %--------------------------------okra data-------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.176\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/testCropped.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:object-prior_test_okra}
\end{figure}
%----------------------------------------------------

\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}). Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150. The corresponding size of the reconstructed volume is 150$\times$150$\times$100. While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.  Projections were obtained using circular cone beam geometry.  %Further, this alignment can be refined following every update of the reconstructed test volume.
The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views. The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed.
%---------------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_green.png}}
\captionsetup{labelformat=empty}
\caption{}
\label{fig:potato3D_test}
     \end{subfigure}
      \caption{Potato 3D dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A}
\end{figure}

\subsection{Simulated measurements from real-life reconstructed volumes}
\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU, consists of six reconstructed
volumes corresponding to six scans of an in-vivo sprout specimen
imaged at its various stages of growth
(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated
from the given volume of size 130$\times$130$\times$130. The ground
truth consists of FDK reconstructed volumes from a set of 1800 view
projections. The test volume was reconstructed from partial set of 45
projections, i.e., $2.5\%$ of the projection views from which ground
truth was reconstructed.\\
%-------------------------sprouts data

\begin{figure}[!h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
\captionsetup{labelformat=empty}
        \caption{}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}\\
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
        right).}
\label{fig:object-prior_test_sprouts}
\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

\textbf{Radio-frequency ablation:} We have used this dataset to
illustrate an application where \textit{both} uniform and spatially-varying priors are
useful. The data~\footnote{Source: Tata Memorial
  Centre~\cite{tmh}, Parel, Mumbai.  This is the national
  comprehensive centre for the prevention, treatment, education and
  research in cancer, and is recognized as one of the leading cancer
  centres in India.} consists of simulated parallel beam measurements of 2D slices
of the organ (liver) at different stages of the scan. The details of this study are presented in the next section.
%--------------------------Results on TMH data--------------------------
%------------------RFA 2 data
\begin{figure}[h!]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 2}
    \end{subfigure}
     \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 3}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 4}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 5}
    \end{subfigure}
              \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 6}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 7}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 8}
    \end{subfigure}     
     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver. Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor. (h) the organ after the ablation: this slice is displayed on a separate intensity scale to enable proper viewing of the region marked in green that shows the after-effects of ablating the tumor.} 
\label{fig:RFA2_test_object-prior}
\end{figure}

@@

@@

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM of the full reconstructed okra volume by various methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline
                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
\textbf{full Volume} & 1 (ideal)                     & 0.83        &  0.87       & \textcolor{red}{0.89}                                                                                   \\ \hline
\end{tabular}
\label{table:okra_ssim_full_volume}
\end{table}
%----------------------------------------------------
\subsubsection{\textbf{Sprouts dataset}}
\label{Sec:sprouts}
 In contrast to the scientific experiment performed for the case of
 the okra where we introduced man-made defects, the changes here are
 purely the work of nature. One of the slices of the reconstructed
 volumes is shown in
 Fig.~\ref{fig:sprouts_3D_results_uniform}. Table~\ref{table:sprouts_ssim_full_volume}
 shows the SSIM of the full reconstructed volumes.  Here again, the
 presence of a unifrom object prior significantly improves the overall
 reconstruction in comparison with the usage of sparsity prior alone.
 The selected 3D ground truth of template volumes, the test volume as
 well as the 3D reconstructions can be seen in the supplementary
 material~\cite{supp_paper}.

 %-----------------------------sprouts 3D results
\begin{figure}[!h]
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
%\captionsetup{labelformat=empty}
        \caption{l1-ls}
     \end{subfigure}\\
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Uniform Prior}
     \end{subfigure}
     \caption{3D reconstruction of sprouts from $2.5\%$ projection
       views (b, c) have poor details (d) no new information detected
       (the prior dominates as can be seen in the blue and red
       regions) and (e) new information detected in the regions of
       interest. The reconstructed volumes can be viewed in the supplementary material
       ~\cite{supp_paper}.} 
\label{fig:sprouts_3D_results_uniform}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

@@

\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights:}

%-----------------------------potato data
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
 \caption{}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
        \caption{}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
        \caption{}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
        \caption{}
\label{fig:potato_test}
      \caption{Potato dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A1}
%-----------------------------potato 2D weights
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_fbp30.png}
        \caption{FBP}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_dct30.png}
        \caption{(l1-ls)-DCT}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_wavelet30.png}
        \caption{(l1-ls)-Haar}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_art30.png}
        \caption{ART}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sart30.png}
        \caption{SART}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sirt30.png}
        \caption{SIRT}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_all_methods30.png}
        \caption{combined}
      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $\boldsymbol{V_\text{low}}$) constructed using different reconstruction methods individually (a-f) and collectively (g) by fusing information from all reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}. The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}. }
\label{fig:weights_map_2Dpotato}
%-----------------------------potato 2D weights
        \includegraphics[width=\textwidth]{../images/potato/2D/fbp.png}
        \caption{FBP}
        \includegraphics[width=\textwidth]{../images/potato/2D/cs_dct.png}
        \caption{(l1-ls)-DCT}
        \includegraphics[width=\textwidth]{../images/potato/2D/cs_wavelet.png}
        \caption{(l1-ls)-Haar}
        \includegraphics[width=\textwidth]{../images/potato/2D/art.png}
        \caption{ART}
        \includegraphics[width=\textwidth]{../images/potato/2D/sart.png}
        \caption{SART}
        \includegraphics[width=\textwidth]{../images/potato/2D/sirt.png}
        \caption{SIRT}
        \includegraphics[width=\textwidth]{../images/potato/2D/weighted_pca_all_methods30.png}
        \caption{combined}
      \caption{(a)-(f):Different reconstructions of~\ref{fig:object-prior_test_potato_A1}(d). The magnitude and sharpness of the artefacts is different for each method. (g) Spatially-Varying-prior method that combines weights-map information from all other methods. The SSIM of these reconstructions is shown in Table.~\ref{table:potato_2D_ssim}.} 
\label{fig:reconstructions_diff_methods}
